### 2019-03-02 papers/journal/experiments.tex
Fixed references and other latex LOG's, Fig and other issues continues

\textbf{{\sattool} (bounded model checker based tool)}:
The enumeration encoding (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.
	%We have implemented the encodings for different variants of VTS (presented in section 6.2) using
The tool is based on CBMC, a successful bounded model checker, for C and C++ programs. 
%
%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
%
It verify property for all the possible states, up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of model is specified by the user and can be  incrementally increased to a desired value.
%
%The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
%CBMC front end accepts

>>>>

{\sattool} \textbf{(bounded model checker based tool)}:
The enumeration encoding (presented in section 6.2) for each variants of VTS is implemented in {\sattool}.
	%We have implemented the encodings for different variants of VTS (presented in section 6.2) using
The tool is based on CBMC, a successful bounded model checker, for C and C++ programs. 
%
%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
%
It verify property for all the possible states, up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of model is specified by the user and can be  incrementally increased to a desired value.
%
%The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
%CBMC front end accepts

### 2019-03-02 papers/journal/intro.tex
Working version for PLOS2 graph Edge Synthesis
Fixed references and other latex LOG's, Fig and other issues continues

\subsection{Vesicle traffic system}
Vesicles were discovered decades ago, in the early 1950s, and major molecules of the vesicle traffic system and their functions were discovered soon after~\cite{wells2005discovery}. These molecules can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments. Below, we give a brief description of the sequence of steps involved in the vesicle transport process. Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model. 
\begin{figure}
	\includegraphics[width=\textwidth]{ankitspaper_schem1.png}
	\label{schematic}
	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments; a source and a target compartment are shown. The symbols used for different molecules involved in vesicle traffic are explained in the key. At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins. Here, the different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck by dynamin. Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex whose one end is attached to the target compartment. At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents into the target compartment. }
\end{figure}

\textbf{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{schematic}.
%
Cargo sorting is performed by cytosolic adaptor proteins. 
Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%
Different adaptor proteins act at different compartments, for eg., vesicle formation at the ER requires the adaptor sec23/24, and AP2 adaptor is used for packaging vesicles at the plasma membrane.
%

@@

\textbf{Vesicle fusion involves two steps:} recognition of the correct target compartment and fusion of the transport vesicle~\cite{schematic}.

>>>>

\subsection{Vesicle traffic system}
Vesicles were discovered decades ago, in the early 1950s, and major molecules of the vesicle traffic system and their functions were discovered soon after~\cite{wells2005discovery}. These molecules can roughly be categorized as budding molecules, whose role is in the formation and budding of transport vesicles from the source compartment, and fusion molecules, which enable fusion of transport vesicles with the target compartments. Below, we give a brief description of the sequence of steps involved in the vesicle transport process. Through this description, we wish to provide a glimpse of the kind of molecular regulatory interactions that we encode in our model.

\begin{figure}
	\includegraphics[width=0.8\textwidth,natwidth=610,natheight=642]{diavts.png}
	\caption{Schematic of the vesicle transport system. Steps involved in vesicle transport between two compartments; a source and a target compartment are shown. The symbols used for different molecules involved in vesicle traffic are explained in the key. At the source compartment, transmembrane cargo proteins are sorted by cytosolic adaptor proteins. Here, the different colours indicate different types of cargo and adaptor proteins. Coat proteins are recruited to the forming vesicle by adaptor proteins. Note here that a single type of coat protein can interact with multiple types of adaptor proteins. Subsequently, the vesicle is pinched off at its neck by dynamin. Once the vesicle has left the source compartment, the coat and adaptor proteins fall off and the vesicle is recognized and bound by a tethering complex whose one end is attached to the target compartment. At the target compartment, the tethered vesicle undergoes fusion, thereby releasing its contents into the target compartment.}
    \label{fig:vts}
\end{figure}

\textbf{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
%
Cargo sorting is performed by cytosolic adaptor proteins. 
Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%
Different adaptor proteins act at different compartments, for eg., vesicle formation at the ER requires the adaptor sec23/24, and AP2 adaptor is used for packaging vesicles at the plasma membrane.
%

@@

\textbf{Vesicle fusion involves two steps:} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.

### 2019-03-02 papers/journal/prelim.tex
Fixed references and other latex LOG's, Fig and other issues continues

We will use lower case variables like $e,r,s$ etc to represent vectors of
Boolean variables, possibly indexed, with multiple dimensions.
%
For example, $r_{ij}$ is a Boolean variable for index $(i,j)$.
%
%
A Boolean variable may take Boolean values $1$ or $0$.
%
The binary Boolean operators $\land$, $\lor$, and $\limplies$ are usually defined.
%
$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over
collection of formulas respectively.
%
We will use the variables and operators to construct Boolean formulas to
encode our problems.
%
An assignment is a map from the variables in the formula to the Boolean values.
%
An assignment may satisfy a formula if the interpretation of Boolean operators
reduce the whole Formula into 1.
%
The problem of finding a satisfying assignment for a Boolean formula is
known to be hard~\cite{sat-hard}.
%

Quantified Boolean formulas(QBFs) also allow quantifiers over Boolean variables.
%
For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
%
The formula says that for both the values of $x$ there is a value of $y$
such that $x \lor y$ is 1.
%
The problem of finding satisfying assignment for QBFs is even harder problem~\cite{qbf-hard}.
%

\subsection{Solvers}
In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use BMC/SMT/QBF solvers to get the satisfying assignments.
%
The modern solvers are result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning(CDCL)~\cite{cdcl}.
%
The QBF solver add support of quantifiers by adding more rules for
quantifiers~\cite{qbf}.

>>>>

We will use lower case variables like $e,r,s$ etc to represent vectors of
Boolean variables, possibly indexed, with multiple dimensions.
%
For example, $r_{ij}$ is a Boolean variable for index $(i,j)$.
%
%
A Boolean variable may take Boolean values $1$ or $0$.
%
The binary Boolean operators $\land$, $\lor$, and $\limplies$ are usually defined.
%
$\Land$ and $\Lor$ are operators that extend $\land$ and $\lor$ over
collection of formulas respectively.
%
We will use the variables and operators to construct Boolean formulas to
encode our problems.
%
An assignment is a map from the variables in the formula to the Boolean values.
%
An assignment may satisfy a formula if the interpretation of Boolean operators
reduce the whole Formula into 1.
%
The problem of finding a satisfying assignment for a Boolean formula is known to be hard~\cite{cook1971complexity}.
%

Quantified Boolean formulas(QBFs) also allow quantifiers over Boolean variables.
%
For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
%
The formula says that for both the values of $x$ there is a value of $y$
such that $x \lor y$ is 1.
%
The problem of finding satisfying assignment for QBFs is even harder problem~\cite{arora2009computational}.
%

\subsection{Solvers}
In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use BMC, SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
%1
The QBF solver add support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
